Implementing simplified INLA into `aghq`

### 2023-06-22 src/dev_sinla/sinla.Rmd
Add warning disclaimer
Missed from previous commit

@@

To understand how this is implemented in `aghq`, the two most important functions are `aghq::marginal_laplace_tmb` and `aghq::sample_marginal`.
`aghq::marginal_laplace_tmb` calculates an object representing $\tilde p(x \, | \, \theta, y)$.
`aghq::sample_marginal` draws samples from this Gaussian, given values of $z$ drawn from a multinomial distribution, in order to evaluate Equation \@ref(eq:pxigiveny).
For a line-by-line walkthrough of how these functions work, see the notebook [Code walkthrough](https://athowes.github.io/elgm-inf/walkthrough.html) (which uses the model from the notebook [Epilepsy example](https://athowes.github.io/elgm-inf/epil.html)).

The goal of this notebook ([Implementing simplified INLA into `aghq`](https://athowes.github.io/elgm-inf/sinla.html)) is to create a new approximation swapping out $\tilde p_\text{G}(x_i \, | \, \theta, y)$ from the above for the simplified INLA approximation $\tilde p_{\text{SINLA}}(x_i \, | \, \theta, y)$ as follows
$$
\tilde p(x_i \, | \, y) = \sum_z \tilde p_{\text{SINLA}}(x_i \, | \, \theta(z), y) \tilde p_\text{LA}(\theta(z) \, | \, y) \omega(z).
$$
We want to do this because the new approximation should be more accurate than taking marginals of a joint Gaussian approximation.
At the extreme, you could just compute a Laplace approximation for each marginal, integrating out all other elements of the latent field, $x_{-i}$, together with the fixed effects $\theta$.
This would be an accurate approach, but not computationally feasible for large models.
What we hope to achieve is an approximation which gets to most of the accuracy benefits of the Laplace approximation approach, but without the high computational cost.

@@

We will use Model 1 from the [Prevalence, ANC, ART model inference case-study](https://athowes.github.io/elgm-inf/prev-anc-art.html) as a running example.
To provide a ground truth to compare the methods that follow to, we generate "gold-standard" inferences using a relatively long run of MCMC as implemented by `tmbstan`.

We begin by loading in testing data, as generated by [`prev-anc-art_sim`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_sim).
`sim_data` contains many replicates of simulated data.
Here we only need one, so will will just take the first as given by:

>>>>

**Warning: this report was created during the process of learning, and for that reason is not concise or well-structured. I would not recommend you reading it, but if you do proceed at your own caution!**

@@

To understand how this is implemented in `aghq`, the two most important functions are `aghq::marginal_laplace_tmb` and `aghq::sample_marginal`.
`aghq::marginal_laplace_tmb` calculates an object representing $\tilde p(x \, | \, \theta, y)$.
`aghq::sample_marginal` draws samples from this Gaussian, given values of $z$ drawn from a multinomial distribution, in order to evaluate Equation \@ref(eq:pxigiveny).
For a line-by-line walkthrough of how these functions work, see the notebook [Code walkthrough](https://athowes.github.io/naomi-aghq/walkthrough.html) (which uses the model from the notebook [Epilepsy example](https://athowes.github.io/naomi-aghq/epil.html)).

The goal of this notebook ([Implementing simplified INLA into `aghq`](https://athowes.github.io/naomi-aghq/sinla.html)) is to create a new approximation swapping out $\tilde p_\text{G}(x_i \, | \, \theta, y)$ from the above for the simplified INLA approximation $\tilde p_{\text{SINLA}}(x_i \, | \, \theta, y)$ as follows
$$
\tilde p(x_i \, | \, y) = \sum_z \tilde p_{\text{SINLA}}(x_i \, | \, \theta(z), y) \tilde p_\text{LA}(\theta(z) \, | \, y) \omega(z).
$$
We want to do this because the new approximation should be more accurate than taking marginals of a joint Gaussian approximation.
At the extreme, you could just compute a Laplace approximation for each marginal, integrating out all other elements of the latent field, $x_{-i}$, together with the fixed effects $\theta$.
This would be an accurate approach, but not computationally feasible for large models.
What we hope to achieve is an approximation which gets to most of the accuracy benefits of the Laplace approximation approach, but without the high computational cost.

@@

We will use Model 1 from the [Prevalence, ANC, ART model inference case-study](https://athowes.github.io/naomi-aghq/prev-anc-art.html) as a running example.
To provide a ground truth to compare the methods that follow to, we generate "gold-standard" inferences using a relatively long run of MCMC as implemented by `tmbstan`.

We begin by loading in testing data, as generated by [`prev-anc-art_sim`](https://github.com/athowes/naomi-aghq/tree/master/src/prev-anc-art_sim).
`sim_data` contains many replicates of simulated data.
Here we only need one, so will will just take the first as given by:
